---
output: html_document
---
```{r data generation, echo = FALSE, results = "hide"}
a<-sample(c(2:5),1)
b<-sample(c(10:30),1)

d<-sample(c('g','b'),1)

dis<- if (d=='g'){
  paste("$Ga(",a,",",b,")$")
} else if (d=='b'){
  paste("$Be(",a,",",b,")$")
}

x1<-seq(0,1,length=1000)
x2<-seq(0,5,length=1000)
x<- if (d=='g'){
  x2
} else if (d=='b'){
  x1
}

dis2<-if(d=='b'){
  dbeta(x1,a,b)
} else if(d=='g'){
  dgamma(x2,a,b)
}

dens<- if (d=='g'){
  paste("\\pi(\\theta|\\textbf{x})=",round((1/factorial(a-1))*b^a,0),"\\theta^{",a-1,"}e^{-",b,"\\theta}, \\theta > 0.")
} else if (d=='b'){
  paste("\\pi(\\theta|\\textbf{x})=",1/((factorial(a-1)*factorial(b-1))/factorial(a+b-1)),"\\theta^",a-1,"(1-\\theta)^",b-1,", 0 < \\theta < 1.")
}

func<- if(d=='g'){
  paste("
        g=function(a){ 

        b=qgamma(0.95+pgamma(a,",a,",",b,"),",a,",",b,")

        (dgamma(a,",a,",",b,")-dgamma(b,",a,",",b,"))^2

        } 

        res=optimise(g, lower=0, upper=qgamma(0.025,",a,",",b,")

        a=res$minimum

        b=qgamma(0.95+pgamma(a,",a,",",b,"),",a,",",b,")")
} else if (d=='b'){
   paste("
        g=function(a){ 

        b=qbeta(0.95+pbeta(a,",a,",",b,"),",a,",",b,")

        (dbeta(a,",a,",",b,")-dbeta(b,",a,",",b,"))^2

        }

        res=optimise(g, lower=0, upper=qbeta(0.025,",a,",",b,")

        a=res$minimum

        b=qbeta(0.95+pbeta(a,",a,",",b,"),",a,",",b,")
        ")
}

   f=function(c1){
d1=qgamma(0.95+pgamma(c1,a,b),a,b)
(dgamma(c1,a,b)-dgamma(d1,a,b))^2
   }
res=optimise(f, lower=0, upper=qgamma(0.025,a,b))
c1=res$minimum 
d1=qgamma(0.95+pgamma(c1,a,b),a,b)

  f2=function(c2){ 
d2=qbeta(0.95+pbeta(c2,a,b),a,b)
(dbeta(c2,a,b)-dbeta(d2,a,b))^2 
}
res=optimize(f2, lower=0, upper=qbeta(0.025,a,b))
c2=res$minimum 
d2=qbeta(0.95+pbeta(c2,a,b),a,b)

sol <- if (d=='g'){
paste("and gives $a$=",round(c1,4), "and $b$=",round(d1,4), ", thus the 95% HDI is (",round(c1,4),",",round(d1,4),").")
} else if (d=='b'){
paste("and gives $a$=",round(c2,4), "and $b$=",round(d2,4), ", thus the 95% HDI is (",round(c2,4),",",round(d2,4),").")
}
```

Question
========
Suppose that a posterior distribution for $\theta$ is a `r dis` distribution, with probability density function $$`r dens`$$

A plot of the distribution is given below. Determine the 95% HDI for $\theta$.

```{r density_plots, echo = FALSE, results = "hide", fig.height = 4, fig.width = 5, fig.path = "", fig.cap = ""}
plot(x,dis2,type='l',xlab='theta',ylab='Density') 
```


Solution
========
The HDI must take the form $c_{\alpha}(a,b)$ if it is to include the values of $\theta$ with the highest probability density. The end-points a and b must satisfy .Unfortunately, there is no simple analytical solution to these equations and so numerical methods have to be employed to find $a$ and $b$.

The `R` code to determine $a$ and $b$ is 

`r func`

`r sol`

Meta-information
================
extype: num
exsolution: 1
exname: highest density intervals 3
extol: 0.01