---
output: html_document
---
```{r data generation, echo = FALSE, results = "hide"}
a<-sample(c(5:50),1)

b<-sample(c(1:15),1)

c<-sample(c(1:10),1)

x1<-seq(0,1,length=1000)

x2<-seq(0,5,length=1000)

d<-sample(c('b','g','e'),1)

dis <- if(d=='b'){
  paste("$Be(1,",a,")$")
} else if (d=='g'){
  paste("$Ga(1,",b,")$")
} else if (d=='e'){
  paste("$Exp(",c,")$")
}

x<-if(d=='b'){
  x1
} else {
  x2
}

dis2<-if(d=='b'){
  dbeta(x1,1,a)
} else if(d=='g'){
  dgamma(x2,1,b)
} else if(d=='e'){
  dexp(x2,c)
}

dens <- if(d=='b'){
  paste(a,"(1-\\theta)^{",a-1,"}, 0 < \\theta < 1.")
} else if (d=='g'){
  paste(b,"e^{-",b,"\\theta}, \\theta > 0.")
} else if (d=='e'){
  paste(c,"e^{-",c,"\\theta}, \\theta > 0.")
}

dens2 <- if(d=='b'){
  paste(a,"(1-\\theta)^{",a-1,"}")
} else if (d=='g'){
  paste(b,"e^{-",b,"\\theta}")
} else if (d=='e'){
  paste(c,"e^{-",c,"\\theta}")
}

sol <- if(d=='b'){
  paste("\\int^b_{0}",dens2,"d\\theta=[-(1-\\theta)^{",a,"}]^{b}_{0}=1-(1-b)^{",a,"}")
} else if(d=='g'){
  paste("\\int^b_{0}",dens2,"d\\theta=[-e^{",-b,"\\theta}]^b_0=-e^{",-b,"b}+e^0=1-e^{",-b,"b}")
} else if (d=='e'){
  paste("\\int^b_{0}",dens2,"d\\theta=[-e^{",-c,"\\theta}]^b_0=-e^{",-c,"b}+e^0=1-e^{",-c,"b}")
}

sol2 <- if (d=='b'){
  paste("1-(1-b)^{",a,"}=1-\\alpha \\implies 1-b=\\alpha^{\\frac{1}{",a,"}} \\implies b=1-\\alpha^{\\frac{1}{",a,"}}")
} else if(d=='g'){
  paste("1-e^{",-b,"b}=1-\\alpha \\implies e^{",-b,"b}=\\alpha \\implies",-b,"b=\\log\\alpha \\implies b=\\frac{1}{",-b,"}\\log\\alpha")
} else if(d=='e'){
  paste("1-e^{",-c,"b}=1-\\alpha \\implies e^{",-c,"b}=\\alpha \\implies",-c,"b=\\log\\alpha \\implies b=\\frac{1}{",-c,"}\\log\\alpha")
}

sol3 <- if(d=='b'){
  paste("(0,1-(0.05^{\\frac{1}{",a,"}})) \\implies (0,",round(1-(0.05)^(1/a),3),")")
} else if (d=='g'){
  paste("(0,\\frac{1}{",-b,"}\\log(0.05)) \\implies (0,",round((-1/b)*log(0.05),3),")")
} else if (d=='e'){
  paste("(0,\\frac{1}{",-c,"}\\log(0.05)) \\implies (0,",round((-1/c)*log(0.05),3),")")
}
```

Question
========
Suppose that the posterior distribution for $\theta$ is `r dis` with probability density function $$\pi(\theta|\textbf{x})=`r dens`$$
A plot of this distribution is given below. Determine the $100(1-\alpha)\%$ HDI for $\theta$. 

Hence calculate the 95% HDI for $\theta$.

```{r density_plots, echo = FALSE, results = "hide", fig.height = 4, fig.width = 5, fig.path = "", fig.cap = ""}
plot(x,dis2,type='l',xlab='theta',ylab='Density') 
```

Solution
========
The HDI must include those values of $\theta$ with highest posterior density and so must take the form $C_{\alpha}(0,b)$. The end point must satisfy $$\int^b_{0} `r dens2`d\theta=1-\alpha.$$ Now $$`r sol`.$$ Hence $$`r sol2`.$$ Therefore, we can work out the 95% HDI for $\theta$ to be $$`r sol3`.$$

Meta-information
================
extype: num
exsolution: 1
exname: highest density intervals
extol: 0.01