---
output: html_document
---

```{r data generation, echo = FALSE, results = "hide"}
require(exams)
#Generate random paramters for our distributions
a<-sample(2:7,1);
b<-sample(2:7,1);
sd<-sample(1:3,1);
mu<-sample(1:5,1);

#Generate values for our x axis
x1<-seq(0,1,length=1000);
x2<-seq(mu-3*sd,mu+3*sd,length=1000);
x3<-seq(0,7,length=1000);

#Randomly choose a distribution to plot
d<-sample(c('b','n','g','u'),1);

dis<-if (d=='b'){
  dbeta(x1,a,b);
} else if (d=='n') {
  dnorm(x2,mu,sd);
} else if (d=='g'){
  dgamma(x3,a,b);
} else if (d=='u'){
  dunif(x3,0,7);
}
dist<-if(d=='b'){
  print("Beta")
} else if (d=="n"){
  print("Normal")
} else if (d=="g"){
  print("Gamma")
} else if (d=="u"){
  print("Uniform")
}

d2<-if(d=='b'){
  sample(c('n','g'),1)
} else if (d=='n'){
  sample(c('b','g'),1)
} else if (d=='g'){
  sample(c('n','b'))
} else {
  sample(c('n','b','g'),1)
}

dis2<-if (d2=='b'){
  dbeta(x1,a,b);
} else if (d2=='n') {
  dnorm(x2,mu,sd);
} else if (d2=='g'){
  dgamma(x3,a,b);
}

#Match our distribution with the relevant axis
x<-if (d=='b') {
  x=x1;
} else if (d=='n') {
  x=x2;
} else {
  x=x3;
}
xt<-if(d2=='b'){
  xt=x1
} else if (d2=='n'){
  xt=x2
} else {
  xt=x3
}

#Calculate the mode of a continuous pdf
x.mode <- x[i.mode <- which.max(dis)]
x.mode2 <-xt[i.mode <- which.max(dis2)]
  
#Generate our questions

questions <- solutions <- explanations <- rep(list(""), 5, sep="")
type <- rep(list("schoice"), 5, sep="")

questions[[1]] <- c(round(max(dis2),2) , round(x.mode2,2) , round(mean(xt)+2.5,2) , "[0,7]" )

questions[[2]] <- c("Beta", "Gamma", "Uniform", "Normal")
    
questions[[3]] <- c(round(pnorm(0.6,mu,sd),2), round(pbeta(0.6,a,b),2), round(pgamma(0.6,a,b),2), round(punif(0.6,0,7),2))

questions[[4]] <- c(round(mu,2), round(a/(a+b),2), round(a/b,2), round(7/2,2))


#Generate our solutions
sol1<-if(d2=='u'){
  questions[[1]][4]
} else {
  questions[[1]][2]
}

sol2<-if(d2=='b'){
  questions[[2]][1]
} else if (d2=='g'){
  questions[[2]][2]
} else if(d2=='u'){
  questions[[2]][3]
} else if(d2=='n'){
  questions[[2]][4]
}

sol3<-if(d2=='n'){
  questions[[3]][1]
} else if (d2=='b'){
  questions[[3]][2]
} else if (d2=='g'){
  questions[[3]][3]
} else if (d2=='u'){
  questions[[3]][4]
}

sol4<- if(d2=='n'){
  questions[[4]][1]
} else if (d2=='b'){
  questions[[4]][2]
} else if (d2=='g'){
  questions[[4]][3]
} else if (d2=='u'){
  questions[[4]][4]
}



#Knit together our solutions
solutions[[1]]<-sol1
solutions[[2]]<-sol2
solutions[[3]]<-sol3
solutions[[4]]<-sol4
solutions[[5]]<-sol5

#Write some explanations
ex1<-print("The mode of the distribution is the value of $\\theta$ at the peak of the distribution")
ex2<- if (d=='n'){
  print("The curve is clearly bellshaped and it is not restricted to the interval [0,1]. It can also take negative values which is a distinguishing feature of the normal distribution")
} else if (d=='b'){
  print("The distribution is restricted to the interval [0,1], which means this is either a beta distribution or a uniform distribution - we can see that the distribution is not flat so this must be a beta distribution ")
} else if (d=='u'){
  print("The distribution is completely flat, therefore this is a uniform distribution")
} else if (d=='g'){
  print("The distribution is not restrained to the interval [0,1], but it cannot take negative values. This must be a gamma distribution")
}
ex3<-print("You should be able to work this out by inspection, as the area under the graph behind 0.6 is the probability")
ex4<-if(d=='u'){
  print("We can see that this distribution is defined in the interval [0,7] by studying the graph, for the uniform distribution, the mean is the midpoint, i.e. 3.5")
} else if (d=='n'){
  print("We can see which value the data is centered around, and a key characteristic of the normal distribution is that the data is symmetric about the mean, so the mean's value should be very close to the value you calculated for the mode")
} else if (d=='b'){
  print("The mean value will be close to the mode, however beta distributions are usually skewed. If the beta distribution is positively skewed, the mean will be bigger than the mode, if the distribution is negatively skewed, the mean will be smaller than the mode")
} else if (d=='g'){
  print("The mean of a gamma distribution is usually not close to the value of the mode. If the gamma distribution is positively skewed, the mean will be greater than the mode, if the distribution is negatively skewed, the mean will be smaller than the mode")
}
ex5<-print("The 95% HDI can be seen by inspection - it is simple to eliminate the impossible intervals, which leaves you with only (at most) two credible intervals, and by inspection you should be able to see the correct solution")

#Knit together our explanations
explanations[[1]]<-ex1
explanations[[2]]<-ex2
explanations[[3]]<-ex3
explanations[[4]]<-ex4
explanations[[5]]<-ex5
```

Question
========
The following plot shows a posterior density $\pi(\theta|x)$. \
```{r density_plots, echo = FALSE, results = "hide", fig.height = 4, fig.width = 5, fig.path = "", fig.cap = ""}
plot(x,dis,type='l',xlab='theta',ylab='Density') 
```

Which family of distributions does this posterior density belong to? Circle a single answer.

|                                     |                            |
|:------------------------------------|----------------------------|
| The posterior distribution is:  	  |`r questions[[2]][1]` / `r questions[[2]][2]` / `r questions[[2]][3]` / `r questions[[2]][4]`   |  

The next plot shows another posterior density $\pi(\theta|x)$. \
```{r densityplots, echo = FALSE, results = "hide", fig.height = 4, fig.width = 5, fig.path = "", fig.cap = ""}
plot(xt,dis2,type='l',xlab='theta',ylab='Density') 
``` 


Circle a single answer for each of the following statements relating to this posterior density.

|                                       |                            |
|:--------------------------------------|----------------------------|
| The posterior mode is: 		               |`r questions[[1]][1]` / `r questions[[1]][2]` / `r questions[[1]][3]` / `r questions[[1]][4]`   |  
| The posterior distribution is:  			   |`r questions[[2]][1]` / `r questions[[2]][2]` / `r questions[[2]][3]` / `r questions[[2]][4]`   |  
| The value of $\Pr(\theta < 0.6 | x)$ is: |`r questions[[3]][1]` / `r questions[[3]][2]` / `r questions[[3]][3]` / `r questions[[3]][4]`   |  
| The posterior mean is:                   |`r questions[[4]][1]` / `r questions[[4]][2]` / `r questions[[4]][3]` / `r questions[[4]][4]`   |  


  
Solution
========
The first posterior distribution is a `r dist` distribution.   

The second posterior distribution has the following properties:

|                                          |                         |
|:-----------------------------------------|-------------------------|
| The posterior mode is: 		               | `r sol1`                |  
| The posterior distribution is:  			   | `r sol2`                |  
| The value of $\Pr(\theta < 0.6 | x)$ is: | `r sol3`                |  
| The posterior mean is:                   | `r sol4`                |  


```{r explanationlist, echo = FALSE, results = "asis"}
answerlist(paste(unlist(explanations), ".", sep = ""), markup = "markdown")
```

Meta-information
================
extype: num
exsolution: 1
exname: prior density
extol: 0.01